COVID-19 Vaccine Acceptance and Hesitancy in Low and Middle Income Countries, and Implications for Messaging

### 2021-05-04 paper_files/figure-latex/mainfigure1-1.tex
drop drive calls
update
no google drive
paper
update files

% Created by tikzDevice version 0.12.3.1 on 2021-03-23 16:52:22
% !TEX encoding = UTF-8 Unicode
\documentclass[10pt]{article}

@@

\path[draw=drawColor,line width= 0.6pt,line join=round] (251.38,434.77) --
	(251.38,440.07);

\path[draw=drawColor,line width= 0.6pt,line join=round] (251.38,437.42) --
	(247.47,437.42);

\path[draw=drawColor,line width= 0.6pt,line join=round] (247.47,434.77) --
	(247.47,440.07);

@@

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (249.43,437.42) circle (  1.96);

@@

\path[draw=drawColor,line width= 0.5pt,line join=round] (390.78, 76.80) --
	(390.78,506.36);
\definecolor{drawColor}{RGB}{153,153,51}

\path[draw=drawColor,line width= 0.6pt,line join=round] (374.36,148.40) --
	(374.36,151.05);

\path[draw=drawColor,line width= 0.6pt,line join=round] (374.36,149.72) --
	(361.75,149.72);

\path[draw=drawColor,line width= 0.6pt,line join=round] (361.75,148.40) --
	(361.75,151.05);
\definecolor{drawColor}{RGB}{68,170,153}

\path[draw=drawColor,line width= 0.6pt,line join=round] (377.73,140.44) --
	(377.73,143.09);

\path[draw=drawColor,line width= 0.6pt,line join=round] (377.73,141.77) --
	(366.20,141.77);

\path[draw=drawColor,line width= 0.6pt,line join=round] (366.20,140.44) --
	(366.20,143.09);
\definecolor{drawColor}{RGB}{153,153,51}

@@

\path[draw=drawColor,line width= 0.6pt,line join=round] (343.26,493.10) --
	(343.26,495.76);
\definecolor{drawColor}{RGB}{68,170,153}

@@

\path[draw=drawColor,line width= 0.6pt,line join=round] (352.72,485.15) --
	(352.72,487.80);
\definecolor{drawColor}{RGB}{153,153,51}

@@

\path[draw=drawColor,line width= 0.6pt,line join=round] (358.27,466.59) --
	(358.27,469.24);
\definecolor{drawColor}{RGB}{68,170,153}

@@

\path[draw=drawColor,line width= 0.6pt,line join=round] (361.42,458.63) --
	(361.42,461.29);
\definecolor{drawColor}{RGB}{153,153,51}

\path[draw=drawColor,line width= 0.6pt,line join=round] (373.49,440.07) --
	(373.49,442.72);

\path[draw=drawColor,line width= 0.6pt,line join=round] (373.49,441.40) --
	(366.42,441.40);

\path[draw=drawColor,line width= 0.6pt,line join=round] (366.42,440.07) --
	(366.42,442.72);
\definecolor{drawColor}{RGB}{68,170,153}

\path[draw=drawColor,line width= 0.6pt,line join=round] (377.19,432.12) --
	(377.19,434.77);

\path[draw=drawColor,line width= 0.6pt,line join=round] (377.19,433.44) --
	(373.05,433.44);

\path[draw=drawColor,line width= 0.6pt,line join=round] (373.05,432.12) --
	(373.05,434.77);
\definecolor{drawColor}{RGB}{153,153,51}

@@

\path[draw=drawColor,line width= 0.6pt,line join=round] (371.75,413.56) --
	(371.75,416.21);
\definecolor{drawColor}{RGB}{68,170,153}

@@

\path[draw=drawColor,line width= 0.6pt,line join=round] (378.16,405.60) --
	(378.16,408.25);
\definecolor{drawColor}{RGB}{153,153,51}

@@

\path[draw=drawColor,line width= 0.6pt,line join=round] (384.91,387.04) --
	(384.91,389.69);
\definecolor{drawColor}{RGB}{68,170,153}

@@

\path[draw=drawColor,line width= 0.6pt,line join=round] (385.45,379.09) --
	(385.45,381.74);
\definecolor{drawColor}{RGB}{153,153,51}

@@

\path[draw=drawColor,line width= 0.6pt,line join=round] (360.01,360.52) --
	(360.01,363.18);
\definecolor{drawColor}{RGB}{68,170,153}

@@

\path[draw=drawColor,line width= 0.6pt,line join=round] (363.16,352.57) --
	(363.16,355.22);
\definecolor{drawColor}{RGB}{153,153,51}

@@

\path[draw=drawColor,line width= 0.6pt,line join=round] (353.37,334.01) --
	(353.37,336.66);
\definecolor{drawColor}{RGB}{68,170,153}

@@

\path[draw=drawColor,line width= 0.6pt,line join=round] (362.29,326.05) --
	(362.29,328.71);
\definecolor{drawColor}{RGB}{153,153,51}

@@

\path[draw=drawColor,line width= 0.6pt,line join=round] (304.77,121.88) --
	(304.77,124.53);
\definecolor{drawColor}{RGB}{68,170,153}

@@

\path[draw=drawColor,line width= 0.6pt,line join=round] (321.73,113.93) --
	(321.73,116.58);
\definecolor{drawColor}{RGB}{153,153,51}

@@

\path[draw=drawColor,line width= 0.6pt,line join=round] (364.46,280.98) --
	(364.46,283.63);
\definecolor{drawColor}{RGB}{68,170,153}

@@

\path[draw=drawColor,line width= 0.6pt,line join=round] (375.34,273.02) --
	(375.34,275.67);
\definecolor{drawColor}{RGB}{153,153,51}

@@

\path[draw=drawColor,line width= 0.6pt,line join=round] (357.61,254.46) --
	(357.61,257.11);
\definecolor{drawColor}{RGB}{68,170,153}

@@

\path[draw=drawColor,line width= 0.6pt,line join=round] (365.99,246.51) --
	(365.99,249.16);
\definecolor{drawColor}{RGB}{153,153,51}

@@

\path[draw=drawColor,line width= 0.6pt,line join=round] (375.23,227.95) --
	(375.23,230.60);
\definecolor{drawColor}{RGB}{68,170,153}

@@

\path[draw=drawColor,line width= 0.6pt,line join=round] (375.45,219.99) --
	(375.45,222.64);
\definecolor{drawColor}{RGB}{153,153,51}

@@

\path[draw=drawColor,line width= 0.6pt,line join=round] (359.79,174.91) --
	(359.79,177.56);
\definecolor{drawColor}{RGB}{68,170,153}

@@

\path[draw=drawColor,line width= 0.6pt,line join=round] (363.81,166.96) --
	(363.81,169.61);
\definecolor{drawColor}{RGB}{153,153,51}

@@

\path[draw=drawColor,line width= 0.6pt,line join=round] (338.69, 95.37) --
	(338.69, 98.02);
\definecolor{drawColor}{RGB}{68,170,153}

@@

\path[draw=drawColor,line width= 0.6pt,line join=round] (357.94, 87.41) --
	(357.94, 90.06);
\definecolor{drawColor}{RGB}{153,153,51}
\definecolor{fillColor}{RGB}{153,153,51}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (368.05,149.72) circle (  1.96);
\definecolor{drawColor}{RGB}{68,170,153}
\definecolor{fillColor}{RGB}{68,170,153}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (371.97,141.77) circle (  1.96);
\definecolor{drawColor}{RGB}{153,153,51}
\definecolor{fillColor}{RGB}{153,153,51}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (349.57,494.43) circle (  1.96);
\definecolor{drawColor}{RGB}{68,170,153}
\definecolor{fillColor}{RGB}{68,170,153}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (356.42,486.48) circle (  1.96);
\definecolor{drawColor}{RGB}{153,153,51}
\definecolor{fillColor}{RGB}{153,153,51}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (361.96,467.91) circle (  1.96);
\definecolor{drawColor}{RGB}{68,170,153}
\definecolor{fillColor}{RGB}{68,170,153}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (366.10,459.96) circle (  1.96);
\definecolor{drawColor}{RGB}{153,153,51}
\definecolor{fillColor}{RGB}{153,153,51}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (369.90,441.40) circle (  1.96);
\definecolor{drawColor}{RGB}{68,170,153}
\definecolor{fillColor}{RGB}{68,170,153}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (375.12,433.44) circle (  1.96);
\definecolor{drawColor}{RGB}{153,153,51}
\definecolor{fillColor}{RGB}{153,153,51}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (375.77,414.88) circle (  1.96);
\definecolor{drawColor}{RGB}{68,170,153}
\definecolor{fillColor}{RGB}{68,170,153}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (381.32,406.93) circle (  1.96);
\definecolor{drawColor}{RGB}{153,153,51}
\definecolor{fillColor}{RGB}{153,153,51}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (386.86,388.37) circle (  1.96);
\definecolor{drawColor}{RGB}{68,170,153}
\definecolor{fillColor}{RGB}{68,170,153}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (386.86,380.41) circle (  1.96);
\definecolor{drawColor}{RGB}{153,153,51}
\definecolor{fillColor}{RGB}{153,153,51}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (363.49,361.85) circle (  1.96);
\definecolor{drawColor}{RGB}{68,170,153}
\definecolor{fillColor}{RGB}{68,170,153}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (365.77,353.90) circle (  1.96);
\definecolor{drawColor}{RGB}{153,153,51}
\definecolor{fillColor}{RGB}{153,153,51}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (360.55,335.33) circle (  1.96);
\definecolor{drawColor}{RGB}{68,170,153}
\definecolor{fillColor}{RGB}{68,170,153}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (369.14,327.38) circle (  1.96);
\definecolor{drawColor}{RGB}{153,153,51}
\definecolor{fillColor}{RGB}{153,153,51}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (306.62,123.21) circle (  1.96);
\definecolor{drawColor}{RGB}{68,170,153}
\definecolor{fillColor}{RGB}{68,170,153}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (323.91,115.25) circle (  1.96);
\definecolor{drawColor}{RGB}{153,153,51}
\definecolor{fillColor}{RGB}{153,153,51}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (368.38,282.30) circle (  1.96);
\definecolor{drawColor}{RGB}{68,170,153}
\definecolor{fillColor}{RGB}{68,170,153}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (377.73,274.35) circle (  1.96);
\definecolor{drawColor}{RGB}{153,153,51}
\definecolor{fillColor}{RGB}{153,153,51}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (362.62,255.79) circle (  1.96);
\definecolor{drawColor}{RGB}{68,170,153}
\definecolor{fillColor}{RGB}{68,170,153}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (369.14,247.83) circle (  1.96);
\definecolor{drawColor}{RGB}{153,153,51}
\definecolor{fillColor}{RGB}{153,153,51}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (378.38,229.27) circle (  1.96);
\definecolor{drawColor}{RGB}{68,170,153}
\definecolor{fillColor}{RGB}{68,170,153}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (377.40,221.32) circle (  1.96);
\definecolor{drawColor}{RGB}{153,153,51}
\definecolor{fillColor}{RGB}{153,153,51}

@@

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (363.49,176.24) circle (  1.96);
\definecolor{drawColor}{RGB}{68,170,153}
\definecolor{fillColor}{RGB}{68,170,153}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (366.86,168.28) circle (  1.96);
\definecolor{drawColor}{RGB}{153,153,51}
\definecolor{fillColor}{RGB}{153,153,51}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (343.04, 96.69) circle (  1.96);
\definecolor{drawColor}{RGB}{68,170,153}
\definecolor{fillColor}{RGB}{68,170,153}

@@

\path[draw=drawColor,line width= 0.5pt,line join=round] (515.39, 76.80) --
	(515.39,506.36);
\definecolor{drawColor}{RGB}{51,34,136}

\path[draw=drawColor,line width= 0.6pt,line join=round] (497.55,140.44) --
	(497.55,143.09);

\path[draw=drawColor,line width= 0.6pt,line join=round] (497.55,141.77) --
	(484.29,141.77);

\path[draw=drawColor,line width= 0.6pt,line join=round] (484.29,140.44) --
	(484.29,143.09);
\definecolor{drawColor}{RGB}{170,68,153}

@@

\path[draw=drawColor,line width= 0.6pt,line join=round] (487.22,148.40) --
	(487.22,151.05);
\definecolor{drawColor}{RGB}{51,34,136}

@@

\path[draw=drawColor,line width= 0.6pt,line join=round] (467.43,485.15) --
	(467.43,487.80);
\definecolor{drawColor}{RGB}{170,68,153}

@@

\path[draw=drawColor,line width= 0.6pt,line join=round] (478.85,493.10) --
	(478.85,495.76);
\definecolor{drawColor}{RGB}{51,34,136}

@@

\path[draw=drawColor,line width= 0.6pt,line join=round] (486.68,458.63) --
	(486.68,461.29);
\definecolor{drawColor}{RGB}{170,68,153}

@@

\path[draw=drawColor,line width= 0.6pt,line join=round] (482.87,466.59) --
	(482.87,469.24);
\definecolor{drawColor}{RGB}{51,34,136}

\path[draw=drawColor,line width= 0.6pt,line join=round] (510.38,432.12) --
	(510.38,434.77);

\path[draw=drawColor,line width= 0.6pt,line join=round] (510.38,433.44) --
	(497.44,433.44);

\path[draw=drawColor,line width= 0.6pt,line join=round] (497.44,432.12) --
	(497.44,434.77);
\definecolor{drawColor}{RGB}{170,68,153}

\path[draw=drawColor,line width= 0.6pt,line join=round] (503.32,440.07) --
	(503.32,442.72);

\path[draw=drawColor,line width= 0.6pt,line join=round] (503.32,441.40) --
	(496.47,441.40);

\path[draw=drawColor,line width= 0.6pt,line join=round] (496.47,440.07) --
	(496.47,442.72);
\definecolor{drawColor}{RGB}{51,34,136}

@@

\path[draw=drawColor,line width= 0.6pt,line join=round] (495.60,405.60) --
	(495.60,408.25);
\definecolor{drawColor}{RGB}{170,68,153}

@@

\path[draw=drawColor,line width= 0.6pt,line join=round] (500.71,413.56) --
	(500.71,416.21);
\definecolor{drawColor}{RGB}{51,34,136}

@@

\path[draw=drawColor,line width= 0.6pt,line join=round] (489.94,326.05) --
	(489.94,328.71);
\definecolor{drawColor}{RGB}{170,68,153}

@@

\path[draw=drawColor,line width= 0.6pt,line join=round] (479.94,334.01) --
	(479.94,336.66);
\definecolor{drawColor}{RGB}{51,34,136}

@@

\path[draw=drawColor,line width= 0.6pt,line join=round] (479.83,299.54) --
	(479.83,302.19);
\definecolor{drawColor}{RGB}{170,68,153}

@@

\path[draw=drawColor,line width= 0.6pt,line join=round] (473.20,307.49) --
	(473.20,310.14);
\definecolor{drawColor}{RGB}{51,34,136}

@@

\path[draw=drawColor,line width= 0.6pt,line join=round] (438.84,113.93) --
	(438.84,116.58);
\definecolor{drawColor}{RGB}{170,68,153}

@@

\path[draw=drawColor,line width= 0.6pt,line join=round] (436.34,121.88) --
	(436.34,124.53);
\definecolor{drawColor}{RGB}{51,34,136}

@@

\path[draw=drawColor,line width= 0.6pt,line join=round] (477.87,273.02) --
	(477.87,275.67);
\definecolor{drawColor}{RGB}{170,68,153}

@@

\path[draw=drawColor,line width= 0.6pt,line join=round] (499.95,280.98) --
	(499.95,283.63);
\definecolor{drawColor}{RGB}{51,34,136}

@@

\path[draw=drawColor,line width= 0.6pt,line join=round] (482.87,246.51) --
	(482.87,249.16);
\definecolor{drawColor}{RGB}{170,68,153}

>>>>

% Created by tikzDevice version 0.12.3.1 on 2021-05-04 13:12:45
% !TEX encoding = UTF-8 Unicode
\documentclass[10pt]{article}

@@

\path[draw=drawColor,line width= 0.6pt,line join=round] (251.27,434.77) --
	(251.27,440.07);

\path[draw=drawColor,line width= 0.6pt,line join=round] (251.27,437.42) --
	(246.92,437.42);

\path[draw=drawColor,line width= 0.6pt,line join=round] (246.92,434.77) --
	(246.92,440.07);

@@

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (249.10,437.42) circle (  1.96);

@@

\path[draw=drawColor,line width= 0.5pt,line join=round] (390.78, 76.80) --
	(390.78,506.36);
\definecolor{drawColor}{RGB}{136,34,85}

\path[draw=drawColor,line width= 0.6pt,line join=round] (374.47,148.40) --
	(374.47,151.05);

\path[draw=drawColor,line width= 0.6pt,line join=round] (374.47,149.72) --
	(361.85,149.72);

\path[draw=drawColor,line width= 0.6pt,line join=round] (361.85,148.40) --
	(361.85,151.05);
\definecolor{drawColor}{RGB}{153,153,51}

\path[draw=drawColor,line width= 0.6pt,line join=round] (377.62,140.44) --
	(377.62,143.09);

\path[draw=drawColor,line width= 0.6pt,line join=round] (377.62,141.77) --
	(366.20,141.77);

\path[draw=drawColor,line width= 0.6pt,line join=round] (366.20,140.44) --
	(366.20,143.09);
\definecolor{drawColor}{RGB}{136,34,85}

@@

\path[draw=drawColor,line width= 0.6pt,line join=round] (343.26,493.10) --
	(343.26,495.76);
\definecolor{drawColor}{RGB}{153,153,51}

@@

\path[draw=drawColor,line width= 0.6pt,line join=round] (352.72,485.15) --
	(352.72,487.80);
\definecolor{drawColor}{RGB}{136,34,85}

@@

\path[draw=drawColor,line width= 0.6pt,line join=round] (358.27,466.59) --
	(358.27,469.24);
\definecolor{drawColor}{RGB}{153,153,51}

@@

\path[draw=drawColor,line width= 0.6pt,line join=round] (361.42,458.63) --
	(361.42,461.29);
\definecolor{drawColor}{RGB}{136,34,85}

\path[draw=drawColor,line width= 0.6pt,line join=round] (375.34,440.07) --
	(375.34,442.72);

\path[draw=drawColor,line width= 0.6pt,line join=round] (375.34,441.40) --
	(367.94,441.40);

\path[draw=drawColor,line width= 0.6pt,line join=round] (367.94,440.07) --
	(367.94,442.72);
\definecolor{drawColor}{RGB}{153,153,51}

\path[draw=drawColor,line width= 0.6pt,line join=round] (376.64,432.12) --
	(376.64,434.77);

\path[draw=drawColor,line width= 0.6pt,line join=round] (376.64,433.44) --
	(371.75,433.44);

\path[draw=drawColor,line width= 0.6pt,line join=round] (371.75,432.12) --
	(371.75,434.77);
\definecolor{drawColor}{RGB}{136,34,85}

@@

\path[draw=drawColor,line width= 0.6pt,line join=round] (371.75,413.56) --
	(371.75,416.21);
\definecolor{drawColor}{RGB}{153,153,51}

@@

\path[draw=drawColor,line width= 0.6pt,line join=round] (378.16,405.60) --
	(378.16,408.25);
\definecolor{drawColor}{RGB}{136,34,85}

@@

\path[draw=drawColor,line width= 0.6pt,line join=round] (384.91,387.04) --
	(384.91,389.69);
\definecolor{drawColor}{RGB}{153,153,51}

@@

\path[draw=drawColor,line width= 0.6pt,line join=round] (385.45,379.09) --
	(385.45,381.74);
\definecolor{drawColor}{RGB}{136,34,85}

@@

\path[draw=drawColor,line width= 0.6pt,line join=round] (360.01,360.52) --
	(360.01,363.18);
\definecolor{drawColor}{RGB}{153,153,51}

@@

\path[draw=drawColor,line width= 0.6pt,line join=round] (363.16,352.57) --
	(363.16,355.22);
\definecolor{drawColor}{RGB}{136,34,85}

@@

\path[draw=drawColor,line width= 0.6pt,line join=round] (353.37,334.01) --
	(353.37,336.66);
\definecolor{drawColor}{RGB}{153,153,51}

@@

\path[draw=drawColor,line width= 0.6pt,line join=round] (362.29,326.05) --
	(362.29,328.71);
\definecolor{drawColor}{RGB}{136,34,85}

@@

\path[draw=drawColor,line width= 0.6pt,line join=round] (304.77,121.88) --
	(304.77,124.53);
\definecolor{drawColor}{RGB}{153,153,51}

@@

\path[draw=drawColor,line width= 0.6pt,line join=round] (321.73,113.93) --
	(321.73,116.58);
\definecolor{drawColor}{RGB}{136,34,85}

@@

\path[draw=drawColor,line width= 0.6pt,line join=round] (364.46,280.98) --
	(364.46,283.63);
\definecolor{drawColor}{RGB}{153,153,51}

@@

\path[draw=drawColor,line width= 0.6pt,line join=round] (375.34,273.02) --
	(375.34,275.67);
\definecolor{drawColor}{RGB}{136,34,85}

@@

\path[draw=drawColor,line width= 0.6pt,line join=round] (357.61,254.46) --
	(357.61,257.11);
\definecolor{drawColor}{RGB}{153,153,51}

@@

\path[draw=drawColor,line width= 0.6pt,line join=round] (365.99,246.51) --
	(365.99,249.16);
\definecolor{drawColor}{RGB}{136,34,85}

@@

\path[draw=drawColor,line width= 0.6pt,line join=round] (375.23,227.95) --
	(375.23,230.60);
\definecolor{drawColor}{RGB}{153,153,51}

@@

\path[draw=drawColor,line width= 0.6pt,line join=round] (375.45,219.99) --
	(375.45,222.64);
\definecolor{drawColor}{RGB}{136,34,85}

@@

\path[draw=drawColor,line width= 0.6pt,line join=round] (359.79,174.91) --
	(359.79,177.56);
\definecolor{drawColor}{RGB}{153,153,51}

@@

\path[draw=drawColor,line width= 0.6pt,line join=round] (363.81,166.96) --
	(363.81,169.61);
\definecolor{drawColor}{RGB}{136,34,85}

@@

\path[draw=drawColor,line width= 0.6pt,line join=round] (338.69, 95.37) --
	(338.69, 98.02);
\definecolor{drawColor}{RGB}{153,153,51}

@@

\path[draw=drawColor,line width= 0.6pt,line join=round] (357.94, 87.41) --
	(357.94, 90.06);
\definecolor{drawColor}{RGB}{136,34,85}
\definecolor{fillColor}{RGB}{136,34,85}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (368.16,149.72) circle (  1.96);
\definecolor{drawColor}{RGB}{153,153,51}
\definecolor{fillColor}{RGB}{153,153,51}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (371.86,141.77) circle (  1.96);
\definecolor{drawColor}{RGB}{136,34,85}
\definecolor{fillColor}{RGB}{136,34,85}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (349.57,494.43) circle (  1.96);
\definecolor{drawColor}{RGB}{153,153,51}
\definecolor{fillColor}{RGB}{153,153,51}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (356.42,486.48) circle (  1.96);
\definecolor{drawColor}{RGB}{136,34,85}
\definecolor{fillColor}{RGB}{136,34,85}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (361.96,467.91) circle (  1.96);
\definecolor{drawColor}{RGB}{153,153,51}
\definecolor{fillColor}{RGB}{153,153,51}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (366.10,459.96) circle (  1.96);
\definecolor{drawColor}{RGB}{136,34,85}
\definecolor{fillColor}{RGB}{136,34,85}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (371.64,441.40) circle (  1.96);
\definecolor{drawColor}{RGB}{153,153,51}
\definecolor{fillColor}{RGB}{153,153,51}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (374.14,433.44) circle (  1.96);
\definecolor{drawColor}{RGB}{136,34,85}
\definecolor{fillColor}{RGB}{136,34,85}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (375.77,414.88) circle (  1.96);
\definecolor{drawColor}{RGB}{153,153,51}
\definecolor{fillColor}{RGB}{153,153,51}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (381.32,406.93) circle (  1.96);
\definecolor{drawColor}{RGB}{136,34,85}
\definecolor{fillColor}{RGB}{136,34,85}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (386.86,388.37) circle (  1.96);
\definecolor{drawColor}{RGB}{153,153,51}
\definecolor{fillColor}{RGB}{153,153,51}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (386.86,380.41) circle (  1.96);
\definecolor{drawColor}{RGB}{136,34,85}
\definecolor{fillColor}{RGB}{136,34,85}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (363.49,361.85) circle (  1.96);
\definecolor{drawColor}{RGB}{153,153,51}
\definecolor{fillColor}{RGB}{153,153,51}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (365.77,353.90) circle (  1.96);
\definecolor{drawColor}{RGB}{136,34,85}
\definecolor{fillColor}{RGB}{136,34,85}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (360.55,335.33) circle (  1.96);
\definecolor{drawColor}{RGB}{153,153,51}
\definecolor{fillColor}{RGB}{153,153,51}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (369.14,327.38) circle (  1.96);
\definecolor{drawColor}{RGB}{136,34,85}
\definecolor{fillColor}{RGB}{136,34,85}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (306.62,123.21) circle (  1.96);
\definecolor{drawColor}{RGB}{153,153,51}
\definecolor{fillColor}{RGB}{153,153,51}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (323.91,115.25) circle (  1.96);
\definecolor{drawColor}{RGB}{136,34,85}
\definecolor{fillColor}{RGB}{136,34,85}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (368.38,282.30) circle (  1.96);
\definecolor{drawColor}{RGB}{153,153,51}
\definecolor{fillColor}{RGB}{153,153,51}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (377.73,274.35) circle (  1.96);
\definecolor{drawColor}{RGB}{136,34,85}
\definecolor{fillColor}{RGB}{136,34,85}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (362.62,255.79) circle (  1.96);
\definecolor{drawColor}{RGB}{153,153,51}
\definecolor{fillColor}{RGB}{153,153,51}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (369.14,247.83) circle (  1.96);
\definecolor{drawColor}{RGB}{136,34,85}
\definecolor{fillColor}{RGB}{136,34,85}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (378.38,229.27) circle (  1.96);
\definecolor{drawColor}{RGB}{153,153,51}
\definecolor{fillColor}{RGB}{153,153,51}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (377.40,221.32) circle (  1.96);
\definecolor{drawColor}{RGB}{136,34,85}
\definecolor{fillColor}{RGB}{136,34,85}

@@

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (363.49,176.24) circle (  1.96);
\definecolor{drawColor}{RGB}{153,153,51}
\definecolor{fillColor}{RGB}{153,153,51}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (366.86,168.28) circle (  1.96);
\definecolor{drawColor}{RGB}{136,34,85}
\definecolor{fillColor}{RGB}{136,34,85}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (343.04, 96.69) circle (  1.96);
\definecolor{drawColor}{RGB}{153,153,51}
\definecolor{fillColor}{RGB}{153,153,51}

@@

\path[draw=drawColor,line width= 0.5pt,line join=round] (515.39, 76.80) --
	(515.39,506.36);
\definecolor{drawColor}{RGB}{170,68,153}

\path[draw=drawColor,line width= 0.6pt,line join=round] (497.34,140.44) --
	(497.34,143.09);

\path[draw=drawColor,line width= 0.6pt,line join=round] (497.34,141.77) --
	(484.29,141.77);

\path[draw=drawColor,line width= 0.6pt,line join=round] (484.29,140.44) --
	(484.29,143.09);
\definecolor{drawColor}{RGB}{68,170,153}

@@

\path[draw=drawColor,line width= 0.6pt,line join=round] (487.22,148.40) --
	(487.22,151.05);
\definecolor{drawColor}{RGB}{170,68,153}

@@

\path[draw=drawColor,line width= 0.6pt,line join=round] (467.43,485.15) --
	(467.43,487.80);
\definecolor{drawColor}{RGB}{68,170,153}

@@

\path[draw=drawColor,line width= 0.6pt,line join=round] (478.85,493.10) --
	(478.85,495.76);
\definecolor{drawColor}{RGB}{170,68,153}

@@

\path[draw=drawColor,line width= 0.6pt,line join=round] (486.68,458.63) --
	(486.68,461.29);
\definecolor{drawColor}{RGB}{68,170,153}

@@

\path[draw=drawColor,line width= 0.6pt,line join=round] (482.87,466.59) --
	(482.87,469.24);
\definecolor{drawColor}{RGB}{170,68,153}

\path[draw=drawColor,line width= 0.6pt,line join=round] (509.51,432.12) --
	(509.51,434.77);

\path[draw=drawColor,line width= 0.6pt,line join=round] (509.51,433.44) --
	(494.83,433.44);

\path[draw=drawColor,line width= 0.6pt,line join=round] (494.83,432.12) --
	(494.83,434.77);
\definecolor{drawColor}{RGB}{68,170,153}

\path[draw=drawColor,line width= 0.6pt,line join=round] (503.64,440.07) --
	(503.64,442.72);

\path[draw=drawColor,line width= 0.6pt,line join=round] (503.64,441.40) --
	(496.36,441.40);

\path[draw=drawColor,line width= 0.6pt,line join=round] (496.36,440.07) --
	(496.36,442.72);
\definecolor{drawColor}{RGB}{170,68,153}

@@

\path[draw=drawColor,line width= 0.6pt,line join=round] (495.60,405.60) --
	(495.60,408.25);
\definecolor{drawColor}{RGB}{68,170,153}

@@

\path[draw=drawColor,line width= 0.6pt,line join=round] (500.71,413.56) --
	(500.71,416.21);
\definecolor{drawColor}{RGB}{170,68,153}

@@

\path[draw=drawColor,line width= 0.6pt,line join=round] (489.94,326.05) --
	(489.94,328.71);
\definecolor{drawColor}{RGB}{68,170,153}

@@

\path[draw=drawColor,line width= 0.6pt,line join=round] (479.94,334.01) --
	(479.94,336.66);
\definecolor{drawColor}{RGB}{170,68,153}

@@

\path[draw=drawColor,line width= 0.6pt,line join=round] (479.83,299.54) --
	(479.83,302.19);
\definecolor{drawColor}{RGB}{68,170,153}

@@

\path[draw=drawColor,line width= 0.6pt,line join=round] (473.20,307.49) --
	(473.20,310.14);
\definecolor{drawColor}{RGB}{170,68,153}

@@

\path[draw=drawColor,line width= 0.6pt,line join=round] (438.84,113.93) --
	(438.84,116.58);
\definecolor{drawColor}{RGB}{68,170,153}

@@

\path[draw=drawColor,line width= 0.6pt,line join=round] (436.34,121.88) --
	(436.34,124.53);
\definecolor{drawColor}{RGB}{170,68,153}

@@

\path[draw=drawColor,line width= 0.6pt,line join=round] (477.87,273.02) --
	(477.87,275.67);
\definecolor{drawColor}{RGB}{68,170,153}

@@

\path[draw=drawColor,line width= 0.6pt,line join=round] (499.95,280.98) --
	(499.95,283.63);
\definecolor{drawColor}{RGB}{170,68,153}

@@

\path[draw=drawColor,line width= 0.6pt,line join=round] (482.87,246.51) --
	(482.87,249.16);
\definecolor{drawColor}{RGB}{68,170,153}
